EGGs are adhesive!\\ An algebraic account of equality saturation

### 2025-09-08 jlamp/jlamp.tex
minima

\paragraph{Left-monogamous hypergraphs}\label{par:lm}
We start by introducing \emph{left-monogamous} hypergraphs \cite{milosavljevic2023string,fritz2023free}, which are the generalization of \emph{term graphs} \cite{corradini2005term,Plu:TGR-ENTCS}.

@@

\begin{defi}
Given an hypergraph $\mathcal{\mathcal{G}}=(E_{\mathcal{G}}, V_{\mathcal{F}}, s_{\mathcal{G}}, t_{\mathcal{G}})$, for every hyperedge $e\in E_{\mathcal{G}}$ with $n_e=\lgh_{V_{\mathcal{G}}}(s_{\mathcal{G}}(e))$ and $m_e=\lgh_{V_{\mathcal{G}}}(t_{\mathcal{G}}(e))$, we can consider the coproduct $(V_e, \{\iota^e_{i}\}_{i=1}^{n_e+m_e})$ of $n_e+m_e$ copies of $1$.
We can further take the coproduct $(V_{\sp(\mathcal{G})}, \{\iota_e\}_{e\in E_{\mathcal{G}}})$ of the family $\{V_{e}\}_{e\in E_\mathcal{G}}$ and define
\[\begin{split}
	s_{\sp(\mathcal{G})} \colon E_{\mathcal{G}}&\to V_{\sp(\mathcal{G})}^\star\\
	e &\mapsto \prod_{i=1}^{n_e} \iota_e(\iota^e_{i}(0))
\end{split}\qquad \begin{split}
	t_{\sp(\mathcal{G})} \colon E_{\mathcal{G}}&\to V_{\sp(\mathcal{G})}^\star\\
	e &\mapsto \prod_{i=n_e+1}^{n_e + m_e} \iota_e(\iota^e_{i}(0))
\end{split} \]
where $0$ is the unique element of the terminal object $1$. 
\marginpar{ovvero?}

>>>>

\paragraph{Left-monogamous hypergraphs}\label{par:lm}
We start by introducing \emph{left-monogamous} hypergraphs \cite{milosavljevic2023string,fritz2023free}, which are the generalization of \emph{term graphs} \cite{CorradiniG05,Plu:TGR-ENTCS}.

@@

\begin{defi}
Given an hypergraph $\mathcal{\mathcal{G}}=(E_{\mathcal{G}}, V_{\mathcal{F}}, s_{\mathcal{G}}, t_{\mathcal{G}})$, for every hyperedge $e\in E_{\mathcal{G}}$ with $n_e=\lgh_{V_{\mathcal{G}}}(s_{\mathcal{G}}(e))$ and $m_e=\lgh_{V_{\mathcal{G}}}(t_{\mathcal{G}}(e))$, we can consider the coproduct $(V_e, \{\iota^e_{i}\}_{i=1}^{n_e+m_e})$ of $n_e+m_e$ copies of $1$.
We can further take the coproduct $(V_{\sp(\mathcal{G})}, \{\iota_e\}_{e\in E_{\mathcal{G}}})$ of the family $\{V_{e}\}_{e\in E_\mathcal{G}}$ and define
\[\begin{split}
	s_{\sp(\mathcal{G})} \colon E_{\mathcal{G}}&\to V_{\sp(\mathcal{G})}^\star\\
	e &\mapsto \prod_{i=1}^{n_e} \iota_e(\iota^e_{i}(0))
\end{split}\qquad \begin{split}
	t_{\sp(\mathcal{G})} \colon E_{\mathcal{G}}&\to V_{\sp(\mathcal{G})}^\star\\
	e &\mapsto \prod_{i=n_e+1}^{n_e + m_e} \iota_e(\iota^e_{i}(0))
\end{split} \]
where $0$ is the unique element of the terminal object $1$.
